Towards a universal-dependency treebank for Kazakh

### 2015-06-18 2015-turklang-kazdep/paper.tex
stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60809 72bbbca6-d526-0410-a7d9-f06f51895060
some stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60810 72bbbca6-d526-0410-a7d9-f06f51895060

\title{Towards a universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^\dagger$ and Jonathan Washington$^\ast$}
\address{$^\dagger$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^\ast$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA}

@@

\subsection{Treebanks}

@@

>>>>

\title{Towards a universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^a$ and Jonathan Washington$^b$}
\address{$^a$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^b$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA}

\keywords{Kazakh, treebank, dependency grammar, universal dependency}

@@

\subsection{Treebanks} % Related work

@@

\section{Conclusions}
